---
title: "Practical Machine Learning - Course Project"
author: "Carlos Cunha"
date: "November 21, 2015"
output: html_document
keep_md: yes
---

# Objectives

<p>
This report was created for **Practical Machine Learning Course** project of the Johns Hopkins University (Bloomberg School of Public Health) Data Science Specialization on Coursera.org, and it aims to present all steps taken to predict in which way a series of execise were performed by subjects - data and definition used herein can be found at **Human Activity Recognition** (HAR) web page (<a href="http://groupware.les.inf.puc-rio.br/har">here</a>).
</p>

<p>
To facilitate the understanding and reproducibility, all files were copied to <a href="https://github.com/ceacunha/PMLProject">this</a> *GitHub repository*. In the repo, one will find:
</p>

- **data directory**: used to archive data files used for training (originaly from <a href="https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv">here</a>) and test (originaly from <a href="https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv">here</a>) of machine learning algorithms;

- **output directory**: used to archive resulting files from prediction process;

- **project_script.R**: original and complete *R programming language* script;

- **report.Rmd**: R markdown file from which this report is created; 

- **report.html**: this report.

# Configuration

<p>
First and foremost, all needed libraries are loaded into *R* environment. Only the *caret* and *randomForest* packages are necessary, the former provides functions and structure widely used for machine learning execution and the latter provides the chosen algorithm implementation.
</p>

``` {r loadingLibraries, message=FALSE, warning=FALSE}
library(caret)
library(randomForest)
```

<p>
Once the *R* environment is set, file directories to store both input and output files are created - *data* and *output* respectively.
</p>

``` {r creatingDirectory, message=FALSE, warning=FALSE}
dir.create("data")
dir.create("output")
```

<p>
As directory structure is placed, input files for training and test machine learning execution are downloaded from HAR web page and stored on *data* directory.
</p>

``` {r downloadingFiles, message=FALSE, warning=FALSE}
trainingFileURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
download.file(trainingFileURL, destfile = "data/training.csv", method = "curl", quiet = TRUE)

testFileURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
download.file(testFileURL, destfile = "data/test.csv",method = "curl", quiet = TRUE)
```

<p>
Finally, with *R* environment, directory structure and files in place, one can turn to machine learning and prediction processes.
</p>

# Training


# Test


# Results